Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elizaveta Kugaevskaia for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.}

### 2019-03-19 paper/paper.tex

\bibitem{} Armenian Ministry of Foreign Affairs. 2018. ``Nagorno-Karabakh Republic (Artsakh).'' https://www.mfa.am/en/nagorno-karabakh-issue/ (accessed on 20 April, 2018).

@@

\bibitem{} Freedom House. 1998. ``Transnistria.'' \textit{Freedom in the World 1998}. freedomhouse.org/report/freedom-world/1998/transnistria (accessed on 26 June, 2017). 
\bibitem{} Freedom House 2009. ``South Ossetia.'' \textit{Freedom in the World 2009}. freedomhouse.org/report/freedom-world/2009/south-ossetia (accessed on 15 March 2019).
\bibitem{} Freedom House 2011. ``South Ossetia.'' \textit{Freedom in the World 2009}. freedomhouse.org/report/freedom-world/2011/south-ossetia (accessed on 15 March 2019).
\bibitem{} Freedom House 2012. ``South Ossetia.'' \textit{Freedom in the World 2012}. freedomhouse.org/report/freedom-world/2012/south-ossetia (accessed on 15 March 2019).
\bibitem{} Freedom House 2015. ``South Ossetia.'' \textit{Freedom in the World 2012}. freedomhouse.org/report/freedom-world/2015/south-ossetia (accessed on 15 March 2019).
\bibitem{} Freedom House 2016. ``South Ossetia.'' \textit{Freedom in the World 2012}. freedomhouse.org/report/freedom-world/2016/south-ossetia (accessed on 15 March 2019).
\bibitem{} Freedom House. 2017. ``Transnistria.'' \textit{Freedom in the World 2017: Populists an Autocrats: The Dueal Threat to Global Democracy}. freedomhouse.org/report/freedom-world/2017/transnistria (accessed on 13 March, 2019).
\bibitem{} Freedom House. 2018. ``South Ossetia.'' \textit{Freedom in the World 2018: Democracy in Crisis}. freedomhouse.org/report/freedom-world/2018/south-ossetia (accessed on 15 March, 2019).
\bibitem{} GADM. 2018. ``GADM Maps and Data (version 3.6).'' https://gadm.org (accessed February 7, 2019).

@@

\bibitem{} Minorities At Risk. 2006a. ``Assessment for Abkhazians in Georgia.'' www.mar.umd.edu/assessment.asp?groupId=37201 (accessed on 5 June, 2017).
\bibitem{} Minorities At Risk. 2006b. ``Assessment for Ossetians (South) in Georgia.'' www.mar.umd.edu/assessment.asp?groupId=37203  (accessed on 6 June, 2017)
\bibitem{} Minorities At Risk. 2006c. ``Assessment for Slavs in Moldova.'' www.mar.umd.edu/assessment.asp?groupId=35902 (accessed on 7 June, 2017).

@@

\bibitem{} National Geophysical Data Center. 2015. ``Version 4 DMSP-OLS Nighttime Lights Time Series.'' National Oceanic and Atmospheric Administration. https://ngdc.noaa.gov/eog/dmsp/downloadV4composites.html (accessed February 6, 2019).

@@

\bibitem{} World Bank. 2018. \textit{World Development Indicators}. http://wdi.worldbank.org (accessed February 27, 2019).

>>>>

\bibitem{} Armenian Ministry of Foreign Affairs. 2018. ``Nagorno-Karabakh Republic (Artsakh).'' \verb!www.mfa.am/en/nagorno-karabakh-issue! (accessed on 20 April, 2018).

@@

\bibitem{} Freedom House. 1998. ``Transnistria.'' \textit{Freedom in the World 1998}. \verb!freedomhouse.org/report/freedom-world/1998/transnistria! (accessed on 26 June, 2017). 
\bibitem{} Freedom House 2009. ``South Ossetia.'' \textit{Freedom in the World 2009}. \verb!freedomhouse.org/report/freedom-world/2009/south-ossetia! (accessed on 15 March 2019).
\bibitem{} Freedom House 2011. ``South Ossetia.'' \textit{Freedom in the World 2009}. \verb!freedomhouse.org/report/freedom-world/2011/south-ossetia! (accessed on 15 March 2019).
\bibitem{} Freedom House 2012. ``South Ossetia.'' \textit{Freedom in the World 2012}. \verb!freedomhouse.org/report/freedom-world/2012/south-ossetia! (accessed on 15 March 2019).
\bibitem{} Freedom House 2015. ``South Ossetia.'' \textit{Freedom in the World 2012}. \verb!freedomhouse.org/report/freedom-world/2015/south-ossetia! (accessed on 15 March 2019).
\bibitem{} Freedom House 2016. ``South Ossetia.'' \textit{Freedom in the World 2012}. \verb!freedomhouse.org/report/freedom-world/2016/south-ossetia! (accessed on 15 March 2019).
\bibitem{} Freedom House. 2017. ``Transnistria.'' \textit{Freedom in the World 2017}. \verb!freedomhouse.org/report/freedom-world/2017/transnistria! (accessed on 13 March, 2019).
\bibitem{} Freedom House. 2018. ``South Ossetia.'' \textit{Freedom in the World 2018}. \verb!freedomhouse.org/report/freedom-world/2018/south-ossetia! (accessed on 15 March, 2019).
\bibitem{} GADM. 2018. ``GADM Maps and Data (version 3.6).'' \verb!gadm.org! (accessed February 7, 2019).

@@

\bibitem{} Minorities At Risk. 2006a. ``Assessment for Abkhazians in Georgia.'' \verb!www.mar.umd.edu/assessment.asp?groupId=37201! (accessed on 5 June, 2017).
\bibitem{} Minorities At Risk. 2006b. ``Assessment for Ossetians (South) in Georgia.'' \verb!www.mar.umd.edu/assessment.asp?groupId=37203!  (accessed on 6 June, 2017)
\bibitem{} Minorities At Risk. 2006c. ``Assessment for Slavs in Moldova.'' \verb!www.mar.umd.edu/assessment.asp?groupId=35902! (accessed on 7 June, 2017).

@@

\bibitem{} National Geophysical Data Center. 2015. ``Version 4 DMSP-OLS Nighttime Lights Time Series.'' National Oceanic and Atmospheric Administration. \verb!ngdc.noaa.gov/eog/dmsp/downloadV4composites.html! (accessed February 6, 2019).

@@

\bibitem{} World Bank. 2018. \textit{World Development Indicators}. \verb!wdi.worldbank.org! (accessed February 27, 2019).
